---
title: "Formatting Dropbox Loggernet Data"
output: html_notebook
---

*You need dropbox access synced in your desktop's file explorer for this to work. If you don't have access, go find lydia! [(or email me)](mailto:lagorgal@si.edu)*

## Add your name in the following format "First Last" [ex. "Lydia LaGorga"]

```{r}
myname = "Lydia LaGorga"
myuser =  Sys.info()["user"]

```

### Run to load libraries, formatting function, and previously unformatted data:

```{r}
# load libraries
library(tidyverse)
library(data.table)
library(zoo)
library(dplyr)
library(purrr)
library(ggplot2)
library(rlist)
library(lubridate)
library(stringr)

#function to make headers consistent
format_head <- function(file) {
  # Read the file, skipping the first 4 rows (device info, headers, units, blank row)
  if (all(grepl("Aquatroll", file, ignore.case = TRUE))){
    data <- fread(file,skip=1, header = TRUE, sep = ",")[-c(1,2)]
  
    }else if(all(grepl("Stage",file, ignore.case = TRUE))==T){
      data <- fread(file,skip=1, header = TRUE)[-c(1,2)]
    }else if(all(grepl("CR10",file, ignore.case = TRUE))==T){
      headers <- c("StatusCode","Year","JD","MT", "SiteName","WaterLvl","Flow_cfs")
      data <- read.table(file, fill=T, sep = ",")
      data <- data[,1:7]
      colnames(data) <- headers
      data <- data %>%
        mutate(time = str_pad(as.character(MT),4, pad = "0")) %>%
        mutate(TIMESTAMP = as.POSIXct(paste0(Year,"-", JD, " ", time), format = "%Y-%j %H%M"))%>%
        mutate(TIMESTAMP = as.character(format.POSIXct(TIMESTAMP, format="%Y-%m-%d %H:%M:%S")))%>%
        select(TIMESTAMP,SiteName,StatusCode,WaterLvl,Flow_cfs)
        
      }else if(all(grepl("Fingerprint",file, ignore.case = TRUE))){
        data <- fread(file,skip=1, header = TRUE)[-c(1,2)]
        header <- c("TIMESTAMP",paste0("nm",as.character(seq(200, 722.5, 2.5))))
        data <- data[ ,-c(2:11)]
        colnames(data)<- header
        data <- data %>% select(c("TIMESTAMP", "nm200", "nm250", "nm400"))
     
     }else{
        data <- fread(file, header = TRUE)
     }
  data <- unique(data)
  return(data)
}

#filepath of previously formatted raw files
raw_loggerdata <- "S:/WatershedScience/Stream_Program/00_Methods/03_Loggernet/WeirDataWorkflow/0_raw_loggerdata/"
#filepath of dropbox
dbfold <- paste0("C:/Users/",myuser,"/Smithsonian Dropbox/", myname,"/WS_data/archived_data/")
#filepath of cr10 files
cr10s <- "S:/WatershedScience/Stream_Program/00_Methods/03_Loggernet/WeirDataWorkflow/00_rawCR10_nonloggernet/"

#read in all raw logger file names
files <- list.files(c(dbfold,cr10s),ignore.case = T, full.names = T)
prevrun <- list.files(raw_loggerdata,ignore.case = T, full.names = F)
matching <- c(paste0(cr10s,prevrun),paste0(dbfold,prevrun))
#only keep files that havent been previously processed
files <- files[files %in% matching == F]

#aquatrolls
indices <- grepl("aquatroll", files, ignore.case = T)
aqtr_files <- files[indices]

#scan
indices <- grepl("fingerprint", files, ignore.case = T)
scan_files <- files[indices]

#stage
indices <- grepl("stage", files, ignore.case = T)
stage_files <- files[indices]

#CR10 stage
indices <- grepl("CR10", files, ignore.case = T)
CR10_files <- files[indices]
```

## Add the type of file you'd like to format first. Options include:

-   Aquatroll Files (aqtr_files)
-   Scan Files (scan_files) \# only 102
-   PT Stage files (stage_files) \# only 101, 102 & 109
-   CR10 Stage files (CR10_files)

## And its associated name:

-   Aquatroll Files ("Aquatroll")
-   Scan Files ("Fingerprint")
-   PT Stage files ("Stage")
-   CR10 Stage files ("CR10Stage")

```{r}
filetype = stage_files
filename = "Stage"
```

# Enter the file type and base file name!

```{r}
files <- filetype #aqtr_files or scan_files or stage_files or CR10_files
file_cat <- filename #Stage, CR10Stage, Fingerprint, Aquatroll
file.copy(files,raw_loggerdata)
formatted <- "S:/WatershedScience/Stream_Program/00_Methods/03_Loggernet/WeirDataWorkflow/1_formatted/"
```

# 101

```{r}
WS_101 <- paste0(files[grepl("101", files)])
WS_101 <- bind_rows(lapply(WS_101, format_head))%>% 
                    mutate(SiteName = "W101") %>% 
                    relocate(SiteName)%>%
                    relocate(TIMESTAMP)
startdate <- substr(as.character(min(WS_101$TIMESTAMP,na.rm=T)),1,10)
stopdate <- substr(as.character(max(WS_101$TIMESTAMP,na.rm=T)),1,10)
fwrite(WS_101, paste0(formatted,"WS_101_",file_cat ,"_",startdate,"_",stopdate,".csv"))
```

# 102

```{r}
WS_102 <- paste0(files[grepl("102", files)])
WS_102 <- bind_rows(lapply(WS_102, format_head))%>% 
  mutate(SiteName = "W102") %>% 
  relocate(SiteName)%>%
  relocate(TIMESTAMP)
startdate <- substr(as.character(min(WS_102$TIMESTAMP,na.rm=T)),1,10)
stopdate <- substr(as.character(max(WS_102$TIMESTAMP,na.rm=T)),1,10)
fwrite(WS_102, paste0(formatted,"WS_102_",file_cat, "_", startdate,"_",stopdate,".csv"))
```

# 109

```{r}
WS_109 <- paste0(files[grepl("109", files)])
WS_109 <- bind_rows(lapply(WS_109, format_head))%>% 
  mutate(SiteName = "W109") %>% 
  relocate(SiteName)%>%
  relocate(TIMESTAMP)
startdate <- substr(as.character(min(WS_109$TIMESTAMP,na.rm=T)),1,10)
stopdate <- substr(as.character(max(WS_109$TIMESTAMP,na.rm=T)),1,10)
fwrite(WS_109, paste0(formatted,"WS_109_",file_cat,"_",startdate,"_",stopdate,".csv"))
```

# 110

```{r}
WS_110 <- paste0(files[grepl("110", files)])
WS_110 <- bind_rows(lapply(WS_110, format_head))%>% 
  mutate(SiteName = "W110") %>% 
  relocate(SiteName)%>%
  relocate(TIMESTAMP)
startdate <- substr(as.character(min(WS_110$TIMESTAMP,na.rm=T)),1,10)
stopdate <- substr(as.character(max(WS_110$TIMESTAMP,na.rm=T)),1,10)
fwrite(WS_110, paste0(formatted,"WS_110_",file_cat,"_",startdate,"_",stopdate,".csv"))
```
